---
title: "report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Goal is to predict the probability of fast sales growth based on the features we have.

First, we use logit models of increasing complexity. Because of its automated feature selection characteristic, LASSO model will also be used. Logit model is not a linear model because we are constraining predicted value to be 0 or 1. Similarly to LASSO, we can put a penalty on how large the coefficients of the logit model should be.

coefficients maybe linear model.

raw variables

 



management related variables - hr.



interactions will be discovered by the RF itself. 

OLS X1: sales_mil_log (coefficient is negative) —> *if sales is larger, then firm is less likely to exit* (default column being equal to 1)

d1 —> first difference of sales, sales on increase or not

train and holdout dataset

training set: 15K observations, 20% default [go out of operation, exit] (the same is true in holdout set as well)

CV - to select best performing predictive model

**classProbs** = TRUE & savedPredictions = TRUE —> tells to CARET that this is binary prediction problem

same seed —> to have exactly the same folds in CV

outcome variable - factor **default** 

family = binomial —> estimate logit models for 2 values (0 & 1)

5 models of increasing complexity. for each fold we want to see RMSE

difference in model RMSE is not large. 

now, I am predicting **probability** 

target is 1 and 0. you are estimating the probability of 1. 

LOGIT lasso. same seed so that we can compare to results of logit. we are trying to select best model out of the LASSO model


```{r pressure, echo=FALSE}

```
